True versus apparent shapes of astrophysical bow shocks

### 2017-07-05 papers/Paper1/sec-quadrics-observations.tex
Choose 9 additional Herschel sources to analyse
The actual data is excluded from the repo, but it can be automatically
downloaded by the scripts in Stellar-Bowshocks-2017/RSG/wget-scripts

We obtain a second sample of bow shocks from a far-infrared survey
\citep{Cox:2012a} of circumstellar shells around asymptotic giant
branch (AGB) stars and cool supergiants, obtained as part of the
\textit{Herschel} MESS (Mass-loss of Evolved StarS) program
\citep{Groenewegen:2011a}.  The survey sources were divided into four
classes, according to the overall shape of the extended emission at
\SI{70}{\um}: ``fermata~\textfermata'', or arcs (Class~I);
``eyes~\faEye'' (Class~II); ``rings~{\Large \(\odot\)}'' (Class~III), and
``irregular~\staveXXV'' (Class~IV).  Of these, only the Class~I sources clearly
correspond to bow shocks, which represent 22 out of 50 total sources.

>>>>

We obtain a second sample of bow shocks from a far-infrared survey
\citep{Cox:2012a} of circumstellar shells around asymptotic giant
branch (AGB) stars and cool supergiants, obtained as part of the
\textit{Herschel} MESS (Mass-loss of Evolved StarS) program
\citep{Groenewegen:2011a}.  The survey sources were divided into four
classes, according to the overall shape of the extended emission at
\SI{70}{\um}: ``fermata~\textfermata'', or arcs (Class~I);
``eyes~\faEye'' (Class~II); ``rings~{\Large \(\odot\)}'' (Class~III), and
``irregular~\staveXXV'' (Class~IV).  Of these, only the Class~I
sources clearly correspond to bow shocks, which represent 23 out of 50
total sources detected with extended emission.  For our sample, we
select the 7 Class~I sources where the shape parameters can be
unambiguously measured, and which are shown in
Figure~\ref{fig:herschel-arc-fits}.  For some of the remaining Class~I
sources (Fig.~1 of \citealp{Cox:2012a}), the bow shock becomes too
diffuse around the ``sides'', so that \(R_{90}\) cannot be reliably
determined (examples include \(\theta\)~Aps and )
